\begin{problem}{Rectangles and Connected Regions}{\textsl{standard input}}{\textsl{standard output}}{3 seconds}{256 megabytes}

Little Petya likes rectangular tables very much. Recently he has received a table consisting of $N$ rows and $M$ columns as a gift from his mother. Each cell of the table is either black or white. The only thing Petya likes more than tables is playing with little Masha. She suggested him to play a game with his new table. The game consists of $Q$ rounds. In each round, Masha chooses a rectangle in the table, and Petya tells her the number of connected regions of cells of the same color in this rectangle (see the definition below). Taking into account the fact that the children can only count to two, \emph{all numbers greater than two are indistinguishable for them} (see the samples for further clarification). Your task is to help Petya answer all Masha's questions.

Two cells of the same color are considered to be in the same connected region inside the given rectangle if there exists a path starting in the first cell and ending in the second one that satisfies the following properties:
\begin{itemize}
\item All cells of the path are of the same color.
\item Every two subsequent cells on this path share a side.
\item All cells of the path belong to the given rectangle.
\end{itemize}

\InputFile
The first line contains two integers $N$ and $M$ ($1 \le N \le 2000$, $1 \le M \le 2000$) which denote the number of rows and columns in the table, respectively. The next $N$ lines contain $M$ characters each and denote Petya's table. Character ``\texttt{1}'' stands for a black cell, and character ``\texttt{0}'' stands for a white cell.

The next line contains an integer $Q$ ($1 \le Q \le 500\,000$) indicating the number of Masha's questions. Each of the next $Q$ lines contains four integers $r_1$, $c_1$, $r_2$ and $c_2$ ($1 \le r_1 \le r_2 \le N$, $1 \le c_1 \le c_2 \le M$) where $(r_1, c_1)$ and $(r_2, c_2)$ are the coordinates of the two opposite corners of rectangle from the current Masha's question.

\OutputFile
You must output $Q$ lines, $i$-th of them must contain the answer for the $i$-th Masha's question. The questions are numbered in the order they appear in the input. \textbf{If the answer for some question is greater than or equal to $3$, you must output $0$ instead.}

\Examples

\begin{example}
\exmp{4 5
01011
10101
01011
00001
5
1 1 2 3
3 1 4 3
3 3 4 5
1 5 4 5
1 4 4 5
}{0
2
2
1
0
}%
\exmp{5 5
11111
11111
11111
11101
11111
3
1 1 3 3
1 1 5 5
3 3 5 5
}{1
2
2
}%
\end{example}

\end{problem}
