\begin{problem}{Data Mining}{\textsl{standard input}}{\textsl{standard output}}{2 seconds}{256 mebibytes}{}

    Wojtek is a programmer at Bytes, Inc.
    He is charged with collecting data, and has a cluster of $n$ serially connected servers at his disposal.
    Server $1$ is connected only to server $2$, server $2$ is connected to servers $1$ and $3$, and so on, up to server $n$, connected only to server $n - 1$.
    Wojtek just learned the upper management is considering cutting funding to his team.
    In particular, they are going to claim all the servers with low amount of storage used.

    Wojtek would like to prevent this from happening, so he resolved to fill his servers with data.
    To do that, he can pick any server, and copy all data on it to one of the servers it is connected to.
    Wojtek has enough time to perform this operation $k$ times before the management makes a decision.
    What is the maximum possible least amount of storage used on any of the servers after Wojtek performs $k$ copy operations?

    To clarify: let the amounts of storage used on the $n$ servers be $s_1, \ldots, s_n$ after Wojtek is done.
    We are interested in maximizing $\min(s_1, \ldots, s_n)$.
    You can assume that the free storage space available on all the servers is effectively unbounded.


\InputFile
  The first line of input contains the integer $k$ ($0 \leq k \leq 10^6)$.
  The second line contains the integer $n$ ($2 \leq n \leq 10\,000)$.
  The third line contains $n$ integers $a_1, \ldots, a_n$ ($1 \leq a_i \leq 10^8$) -- the initial amounts of storage used on the servers.

\OutputFile

Output the maximum possible least amount of storage used on any of the servers 
after Wojtek performs $k$ copy operations. Because the answer can be very big, 
output it modulo $10^9 + 7$.

\Examples
\begin{example}
\exmp{
5
5
42 1 3 3 6
}{
43
}%
\end{example}

\Note

    For the above example, Wojtek can perform the following sequence of copy operations:
    \begin{itemize}
        \item server $2$ to server $1$,
        \item server $1$ to server $2$,
        \item server $2$ to server $3$,
        \item server $3$ to server $4$,
        \item server $4$ to server $5$.
    \end{itemize}
    The final amounts of storage used on each server are $43, 44, 47, 50$ and $56$, respectively.


\end{problem}
