\begin{problem}{String Problem}{stdin}{stdout}{4 seconds}{512 megabytes}

Search requests are great! An edit box and a search button order the whole internet in front of you, in search of an answer. Millions of search requests are carefully stored to allow answering the questions faster. To make a search, even faster users receive hints as they type the question. But what if we know nothing about the user?

You are working on an algorithm that will order two request hints in lexicographical order. Well, almost lexicographical.

Users can make typos while entering a search request. We say that string $A$ is \emph{almost less} than string $B$ if string $A$ is lexicographically less than string $B$, or we can replace one letter in $A$ with another lowercase English letter so that the resulting string is lexicographically less than string $B$.

You are given a set of $N$ words which are the search hints. Calculate the number of ordered pairs of hints in which the first hint is \emph{almost less} than the second hint. The order of the words matters: if two hints are \emph{almost less} than each other, you need to count both ordered pairs.

\InputFile
The first line of input contains one integer $N$ ($1 \le N \le 10^6$), the number of given search hints.
Each of the next $N$ lines contains a single word which is a search hint.
Words consist only of lowercase English letters, and their total length does not exceed $10^6$ characters.


\OutputFile
Print one integer: the number of pairs of search hints such that the first one is \emph{almost less} than the second.


\Examples

\begin{example}
\exmp{3
a
b
c
}{4
}%
\exmp{2
aab
aba
}{2
}%
\exmp{2
aa
aaa
}{1
}%
\end{example}

\end{problem}
