\begin{problem}{Dice}{stdin}{stdout}{1 second}{512 megabytes}

You are given a cube.
Each of its six faces has an integer from $1$ to $6$ corresponding to it.
Different faces have different integers corresponding to them.

You are also given a hexomino: a planar polygon made of six equal-sized squares connected edge-to-edge.
Each of its six squares also has an integer from $1$ to $6$ corresponding to it.
Again, different squares have different integers corresponding to them.

Check if it is possible to fold the given hexomino into a cube which could be then rotated in such a way that the numbering of its faces corresponds to the numbering of the faces of the given cube.
It is allowed to fold the hexomino along the borders of the squares, but it is not allowed to make cuts.


\InputFile
The first line of input contains the integers corresponding to the faces of the cube.
The faces are listed in the following order: front, back, left, right, top, bottom.

After that, the hexomino is given as an array of $K \times N$ squares:
each of next $K$ lines contains exactly $N$ digits from $0$ to $6$ without spaces.
Zeroes denote empty cells, and non-zero digits denote the cells of the hexomino.

You may assume that each row and each column of the array contains at least one non-zero digit, each non-zero digit from $1$ to $6$ can be found in the array exactly once, and non-zero digits form an edge-connected polygon.


\OutputFile
Print ``\texttt{Yes}'' if it is possible to obtain the given cube by folding the given hexomino, and ``\texttt{No}'' otherwise.


\Examples

\begin{example}
\exmp{1 2 3 4 5 6
0100
3546
0200
}{Yes
}%
\exmp{1 6 2 5 3 4
1020
3546
}{No
}%
\end{example}

\end{problem}
