\begin{problem}{Cycles with Common Vertex}{\textsl{standard input}}{\textsl{standard output}}{2 seconds}{256 megabytes}

Recently Ksyusha bought $N$ graphs, the $i$-th of them is a chain consisting of $c_i$ vertices (see the definition below). In addition to them, Ksyusha is a happy owner of the Super-vertex. Ksyusha added edges from the endpoints of each chain to the Super-vertex. As a result, she obtained $N$ cycles intersecting in Super-vertex, the $i$-th of these cycles consists of $(c_{i} + 1)$ vertices.

Ksyusha decided to color each vertex of her graph into either black or white. She calls a graph good if the shortest distance between any two vertices colored black is greater than or equal to $K$. Now Ksyusha is wondering what is the maximum number of vertices that can be colored black so that the graph would still remain good?

\InputFile
The first line contains two integers $N$ and $K$ ($1 \le N \le 100\,000$, $2 \le K \le 100\,000$) which denote the number of chains and the restriction on the distance between vertices colored black. The next line contains a sequence of $N$ integers $c_i$ ($K \le c_i \le 10^9$) which denote the lengths of chains.


\OutputFile
Print the maximum number of vertices that can be colored black. 

\Examples

\begin{example}
\exmp{2 3
3 3
}{2
}%
\exmp{2 3
6 9
}{5
}%
\end{example}

\Note
A chain consisting of $V$ ($V > 1$) vertices is a graph where all vertices except two have degree $2$. The remaining two vertices have degree $1$ and are called the endpoints of the chain.

\end{problem}
