\begin{problem}{Permutation Cube}{\textsl{standard input}}{\textsl{standard output}}{3 seconds}{256 megabytes}

Recently Ksyusha installed the game ``Permutation Cube'' on her computer. The rules are the following. At the beginning, three permutations $X_i$, $Y_i$ and $Z_i$ of the set $1$, $2$, $\dots$, $N$ are generated. On the each move, the player can perform one of two actions:
\begin{itemize}
\item Move the cursor to an arbitrary point $(u, v, t)$ where $1 \le u, v, t \le N$. The player must pay a fee of $1$ coin.
\item If the current cursor position is $(u, v, t)$, move the cursor to the point $(X_u, Y_v, Z_t)$ for free.
\end{itemize}
The aim of the game is to visit all $N^3$ points $(u, v, t)$ such that $1 \le u, v, t \le N$. At the beginning, the cursor is not placed anywhere. Find the minimum number of coins that Ksyusha will need to pay in order to win.

Recall that a \emph{permutation} is an ordered arrangement of the set of numbers $1$, $2$, $\dots$, $N$ in which each of these numbers occurs exactly once.

\InputFile
The first line contains an integer $N$, the size of playing field ($1 \le N \le 30\,000$). The next three lines contain permutations $X_i$, $Y_i$ and $Z_i$, one per line. It is guaranteed that each of these lines contains a valid permutation of the numbers $1$, $2$, $\dots$, $N$. Consecutive elements of each permutation are separated by spaces.

\OutputFile
Print the minimum number of coins needed to be paid in order to win the game.

\Examples

\begin{example}
\exmp{3
1 2 3
3 1 2
2 1 3
}{6
}%
\exmp{3
1 3 2
2 3 1
3 1 2
}{6
}%
\end{example}

\end{problem}
